---
title: "Gender Essentialism Draft"
output: html_document
---

```{r}

data_essentialism <- read.csv("~/Desktop/Essentialism_in_trans_data_OSF.csv", sep=";")
library(ggplot2)

```

Manipulate data to combine Same Sex columns and Opposite Sex columns
*Note: I am unable o solve this issue of merging/combining columns so this function won't run properly
```{r}
data_essentialism$samesexscore<-NA
data_essentialism$oppsexscore<-NA
```


```{r}
colnames(data_essentialism)
library(dplyr)
data_essentialism$samesexscore<-rowSums(data_essentialism[,c("SameSexBoyHair" , "SameSexBoyBall", "SameSexBoyDress", "SameSexBoyDoll","SameSexGirlHair", "SameSexGirlBall", "SameSexGirlDress", "SameSexGirlDoll")])

data_essentialism$oppsexscore<-rowSums(data_essentialism[,c("OppSexBoyHair" , "OppSexBoyBall", "OppSexBoyDress", "OppSexBoyDoll","OppSexGirlHair", "OppSexGirlBall", "OppSexGirlDress", "OppSexGirlDoll")])

```


rename Conditions to match participant group
```{r}
class(data_essentialism$Condition)
data_essentialism$Condition[data_essentialism$Condition =="1"] <-"Control"
data_essentialism$Condition[data_essentialism$Condition =="2"] <-"Transgender Children"
data_essentialism$Condition[data_essentialism$Condition =="3"] <-"Siblings"
```

rename participant column 
```{r}
names(data_essentialism)[names(data_essentialism) == 'SubNum_deid'] <- 'participant'
```
Assess samesex and oppsex score for analysis and graphing
```{r}
data_essentialism$SexMatchedRearing<- NA
data_essentialism$OtherSexRearing<- NA
divide8<- function(column)
  column /8
data_essentialism$SexMatchedRearing<- divide8(data_essentialism$samesexscore)
data_essentialism$OtherSexRearing<- divide8(data_essentialism$oppsexscore)
```

Run ANOVA for data essentialism in Sex-Matched and Other-Sex Rearing Conditions
```{r}
anovaSexMatched<-aov(SexMatchedRearing~ Condition, data=data_essentialism)
summary(anovaSexMatched)
library(report)
report(anovaSexMatched)
```

```{r}
anovaOtherSex<-aov(OtherSexRearing~ Condition, data=data_essentialism)
report(anovaOtherSex)
```

Run T-tests to see if Sex-Matched and Other-Sex Rearing differs by gender of participants
```{r}
ttestSexMatched<-t.test(SexMatchedRearing~GenderID, data=data_essentialism, var.equal=TRUE)
report(ttestSexMatched)

```

```{r}
ttestOtherSex<-t.test(OtherSexRearing~GenderID, data=data_essentialism, var.equal=TRUE)
report(ttestOtherSex)
```

Run a Correlation between age and Sex-Matched and Other-Sex Rearing
```{r}
CorTestSexMatched<-cor.test(data_essentialism$AgeYrs, data_essentialism$SexMatchedRearing)
report(CorTestSexMatched)
```

```{r}
CorTestOtherSex<-cor.test(data_essentialism$AgeYrs, data_essentialism$OtherSexRearing)
report(CorTestOtherSex)
```


Graph data for each participant group. 
```{r}
library(ggplot2)
library(wesanderson)
library(hrbrthemes) 
SexandOtherGraph<-ggplot(data_essentialism, aes(SexMatchedRearing, OtherSexRearing, color=Condition))+geom_point()+ xlim(0, 1.00)+ ylim(0, 1.00)+ geom_jitter()+ theme_classic()+ geom_smooth(method="lm", aes(fill=Condition))+ scale_color_manual(values=wes_palette(n=3, name="FantasticFox1"))+scale_fill_manual(values=wes_palette(n=3, name="FantasticFox1"))

```
 Graph Age and Sex Matched/Other Sex Rearing 
```{r}
AgeGraphSame<-ggplot(data_essentialism, aes(AgeYrs, SexMatchedRearing))+geom_jitter()+geom_smooth(method="lm", aes(fill=Condition))+ theme_minimal() + scale_color_manual(values=wes_palette(n=3,name="FantasticFox1"))+scale_fill_manual(values=wes_palette(n=3, name="FantasticFox1"))

AgeGraphSame+facet_wrap(~Condition)
```

```{r}
AgeGraphOther<-ggplot(data_essentialism, aes(AgeYrs, OtherSexRearing))+geom_jitter()+ geom_smooth(method="lm", aes(fill=Condition))+ theme_minimal() + scale_color_manual(values=wes_palette(n=3,name="FantasticFox1"))+scale_fill_manual(values=wes_palette(n=3, name="FantasticFox1"))

AgeGraphOther+facet_wrap(~Condition)
```
 Graph Gender and Sex Matched/Other Sex Rearing 
```{r}
GenderGraphSame<-ggplot(data_essentialism, aes(GenderID,SexMatchedRearing, color=Condition))+geom_jitter()+ geom_smooth(method="lm", aes(fill=Condition))+ theme_minimal()+scale_color_manual(values=wes_palette(n=3,name="FantasticFox1"))+scale_fill_manual(values=wes_palette(n=3, name="FantasticFox1"))

GenderGraphSame+facet_wrap(~Condition)
```

```{r}
GenderGraphOther<-ggplot(data_essentialism, aes(GenderID,OtherSexRearing, color=Condition))+geom_jitter()+ geom_smooth(method="lm", aes(fill=Condition))+ theme_minimal()+scale_color_manual(values=wes_palette(n=3,name="FantasticFox1"))+scale_fill_manual(values=wes_palette(n=3, name="FantasticFox1"))


GenderGraphOther+facet_wrap(~Condition)

```

